Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-06-06 SDSS Presentation/SDSS Presentation.Rmd
Updates with screenshots

.medium.emph[
+ As small rural towns, traditionally, do not have access:
     + Data scientists 
     + Ability to easily leverage data collected locally to support decisions

@@

.medium.emph[
+ Create a central place for the excess of data to be conveyed in a single comprehensive visual.
    + We will utilize Parallel Coordinate Plot (PCPs)
+ Create a map feature that will allow for town leaders to understand the distance of essential QoL components (e.g. Fire Dept, Schools, etc.)
+ Add an overview of town general basics related to the seven QoL factors.
]
--

@@

.medium.emph[
+ We will assess our visualizations to determine which strategies for user interface and interactive graphics design are most useful to empower town leaders to make discoveries in publicly available data assembled with a focus on items that impact rural quality of life.
]

@@

.center[
<img src="images/version1.png" width="75%"/>
]

@@

.center[
<img src="images/version2.png" width="75%"/>
]

@@

.center[
<img src="images/version3.png" width="50%"/>
]

@@

.large.emph[
+ Map (Town's closest services)
]

.large.emph[
+ Vital Statistics (Town-centric and county level)
]
--
 <br>

.large.emph[
+ Parallel Coordinate Plot with objective measures related to the QoL Survey
]

>>>>

.small.emph[
+ As small rural towns, traditionally, do not have access:
     + Data scientists 
     + Ability to easily leverage data collected locally to support decisions

@@

.small.emph[
+ Create a central place for the excess of data to be conveyed in a single comprehensive visual.
    + We will utilize Parallel Coordinate Plot (PCPs)
+ Create a map feature that will allow for town leaders to understand the distance of essential QoL components (e.g. Fire Dept, Schools, etc.)
+ Add an overview of town general basics related to the seven QoL factors.
]
--

@@

.small.emph[
+ We will assess our visualizations to determine which strategies for user interface and interactive graphics design are most useful to empower town leaders to make discoveries in publicly available data assembled with a focus on items that impact rural quality of life.
]

@@

.center[
<img src="images/version1.png" width="80%"/>
]

@@

.center[
<img src="images/version2.png" width="52%"/>
]

@@

.center[
<img src="images/version3.png" width="60%"/>
]

@@

- Map (Town's closest services)

.center[
<img src="images/map.png" width="60%"/>
]

- Vital Statistics (Town-centric and county level)

.column[
<img src="images/vital1.png" width="50%"/>
<img src="images/vital2.png" width="50%"/>
]

- Parallel Coordinate Plot with objective measures related to the QoL Survey

.center[
<img src="images/pcp.png" width="75%"/>
]

[Smart Connected Communities Dashbaord](https://shiny.srvanderplas.com/Smart-Connected-Communities/)
---
# Dashboard Philosophy
